---
output: 
  pagedown::html_paged:
    css: www/styles_prevvisit.css
    toc: false
    numbered_sections: false
    number_sections: false
params:
  year: "2018"
  park: "MABI"
  plot: "MABI-001"
  

---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(pagedown)
#params <- data.frame(park = "MABI", year = 2018, plot = "MABI-001")
```

### Previous Visit and Stand Data: <span style="font-weight:bold;">`r paste0(params$plot, '-', params$year)`</span> {-}

<hr>

```{r import, include = FALSE}
#forestNETN::importData()
source("Previous_Visit_FieldForms_NETN_compile.R")
```

#### Plot and Visit Notes {-} 
```{r visit_notes, child = "PrevVisit_1A_Visit_Notes.Rmd"}
```

```{r stand, child = "PrevVisit_1B_Stand_Data.Rmd"}
```


### Previous Tree Data: <span style="font-weight:bold;">`r paste0(params$plot, '-', params$year)`</span> {.page-break-before} 

<hr>

### Tree Measurements {-}

#### Tree Map {-}
```{r treemap, out.width = "80%"}
plotTreeMap(park = params$park, from = as.numeric(params$year), 
            to = as.numeric(params$year), plotName = params$plot)
```

#### Tree Data {-}

#### Tree Conditions {-}

#### Tree Foliage {-}


### Previous Microplot Data: <span style="font-weight:bold;">`r paste0(params$plot, '-', params$year)`</span> {.page-break-before} 

<hr>

### Microplot Data {-} 

#### Saplings {-}

#### Seedlings {-}

#### Shrubs {-}


### Previous Quadrat Data: <span style="font-weight:bold;">`r paste0(params$plot, '-', params$year)`</span> {.page-break-before} 

<hr>

### Quadrats {-} 

#### Quadrat Data {-}

#### Quadrat Species {-}

#### Additional Species {-}


### Previous CWD and Soils Data: <span style="font-weight:bold;">`r paste0(params$plot, '-', params$year)`</span> {.page-break-before} 

<hr>

### Coarse Woody Debris {-} 

### Soils {-} 


### Previous Photopoints: <span style="font-weight:bold;">`r paste0(params$plot, '-', params$year)`</span> {.page-break-before} 

<hr>


