---
output: 
  pagedown::html_paged:
    css: www/styles_weeklyQC.css
    toc: false
    numbered_sections: false
    number_section: false
params:
  year: "2018"
  park: "MABI"
  plot: "MABI-001"
  

---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(pagedown)
#params <- data.frame(park = "MABI", year = 2018, plot = "MABI-001")
```

Previous Visit Data: <span style="font-weight:bold;">`r paste0(params$plot, '-', params$year)`</span> {-}
--------------------------------------------------

```{r import, include = FALSE, cache = FALSE}
#forestNETN::importData()
source("Previous_Visit_FieldForms_NETN_compile.R")
```

### Stand and Visit Data {-}

---

#### Visit Notes {-}
```{r visit_notes, child = "PrevVisit_1A_Visit_Notes.Rmd"}
```

#### Stand Data {-}
```{r stand, child = "PrevVisit_1B_Stand_Data.Rmd"}
```


### Tree Measurements {-} {.page-break-before}
#### Tree Map {-}

#### Tree Data {-}

#### Tree Conditions {-}

#### Tree Foliage {-}

### Microplot Data {-} {.page-break-before}
#### Saplings {-}

#### Seedlings {-}

#### Shrubs {-}


### Quadrats {-} {.page-break-before}
#### Quadrat Data {-}

#### Quadrat Species {-}

#### Additional Species {-}


### Coarse Woody Debris {-} {.page-break-before}


### Soils {-} {.page-break-before}

### Photopoints {-} {.page-break-before}

