---
output: 
  html_document:
    css: www/styles_weeklyQC.css
    anchor_sections: FALSE
    includes:
        in_header: "header_manual.html"
params:
  week_start: "2023-07-16"
  cycle_latest_num: 4
  locType: 'all'

---
Weekly QC Report for week starting: <span style="font-weight:bold;">`r params$week_start`</span> {.tabset .tabset-pills}
--------------------------------------------------
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

```{r import, include = FALSE, cache = FALSE}
forestMIDN::importData()
#forestMIDN::importCSV(path = "D:/NETN/R_Dev/data", zip_name = "MIDN_Forest_20220316.zip") # Import from dev after refresh and PR merge
```

```{r deps, include = FALSE}
library(forestMIDN)
library(tidyverse)
library(lubridate)
library(knitr)
library(kableExtra)
```

```{r set_params, echo = FALSE, include = TRUE}
curr_year <- year(params$week_start)
week_start <- as_date(params$week_start)
cycle_latest <- paste0("cycle_", params$cycle_latest_num)
cycle_latest_num <- params$cycle_latest_num
cycle_prev <- paste0("cycle_", params$cycle_latest_num-1)
cycle_prev_num <- params$cycle_latest_num - 1
loc_type <- params$locType
```

```{r compile}
source("Weekly_QC_functions.R")
source("Weekly_QC_compile_MIDN.R")
```

### QC Checks {.tabset}
#### Summary {.tabset}
```{r visits_checked, echo = F, results = 'hide'}
visits_checked <- noquote(paste(sort(new_evs_list), collapse = ", "))
```
The following plot visits were checked for this report: <br>
<br>
<div class = 'indent'>`r visits_checked`</div>
<br>
The table below documents the Quality Control checks that were performed and number of records returned that require further review by database tab. If any records are returned for a given database tab, a separate tab corresponding to that tab reports the data that require further review. Note that this report also compiles priority forest pest/pathogen and invasive plant early detection species detected in a plot. 

```{r QC_results}
QC_check_table
```
<br>
<br>


```{r visit_notes, echo = FALSE, eval = include_visit_notes, results = 'asis'}
cat("#### Visit Notes {.tabset}", "\n")
if(include_visit_notes == TRUE){
visit_table
  }
```
<br>
<br>

```{r plot_tab, echo = FALSE, eval = include_plot_tab, results = 'asis'}
cat("### Plot & Visit Data {.tabset}", "\n")

```

```{r plot_tables, echo = FALSE, eval = include_plot_tab}
check_null(plot_na_table)

check_null(miss_dir_table)
```


```{r stand_tab, echo = FALSE, eval = include_stand_tab, results = 'asis'}
cat("### Stand {.tabset}", "\n")

```

```{r stand_tables, echo = FALSE, eval = include_stand_tab}
check_null(stand_pm_table)

check_null(stand_str_table)

check_null(microtop_table)

check_null(DBI_1_table)

check_null(DBI_diff_table)

check_null(stand_dist_table)

check_null(stand_ht_99_table)

check_null(stand_ht_comp_table)

```

```{r tree_tab, echo = FALSE, eval = include_tree_tab, results = 'asis'}
cat("### Tree {.tabset}", "\n")

```

```{r tree_tables, echo = FALSE, eval = include_tree_tab}
check_null(tree_data_pm_table)

check_null(status_table)

check_null(elev_mort_table)

check_null(em_spp_table)

check_null(crown_table)

check_null(zoinks_table)

check_null(tree_dbh_table)

check_null(tree_dbhnz_table) # new for 2023

check_null(fol_maj_table)

check_null(trcond_spp_table)

check_null(pest_table)

```

```{r micro_tab, echo = FALSE, eval = include_micro_tab, results = 'asis'}
cat("### Microplot {.tabset}", "\n")

```

```{r micro_tables, echo = FALSE, eval = include_micro_tab}
check_null(micro_check3_table)

check_null(micro_ns_table)

check_null(sap_pm_table)

check_null(sap_dup_tag_table)

check_null(sap_status_table)

check_null(sap_data_pm_table) # New for MIDN

check_null(sap_elev_mort_table) # New for MIDN

check_null(sap_em_spp_table) # New for MIDN

check_null(zoinks_sap_table) # New for MIDN

check_null(sap_dbh_table) # New for MIDN

check_null(sap_dbhnz_table) # New for 2023

check_null(sap_stat_table) # New for 2023

check_null(shrub_pm_table)

check_null(shrub_ss_sq_table)

check_null(shrub_0cov_table)

```

```{r quad_tab, echo = FALSE, eval = include_quad_tab, results = 'asis'}
cat("### Quadrat {.tabset}", "\n")

```

```{r quad_tables, echo = FALSE, eval = include_quad_tab}
check_null(quad_ns_table)

check_null(quad_ns_missing_notes_table)

check_null(quad_data_pm_table)

check_null(quad_spp_pm_table)

check_null(quad_seed_pm_table) # Updated for MIDN

check_null(quad_0cov_table) # Updated quad names for MIDN

check_null(quad_sq_data_table)

check_null(quad_sq_spp_table)

check_null(seed_pm_table) # Updated for MIDN

check_null(seed_ss_sq_table) # Updated for MIDN

check_null(seed_0tally_table) # Updated for MIDN

check_null(seeds_99_table) # Updated for MIDN

check_null(quad_tramp_table)

check_null(quad_tramp_all_table) # new for 2023
```


```{r addspp_tab, echo = FALSE, eval = include_addspp_tab, results = 'asis'}
cat("### Additional Species {.tabset}", "\n")

```

```{r addspp_tables, echo = FALSE, eval = include_addspp_tab}
check_null(addspp_ns_table)

check_null(addspp_ns_missing_notes_table)

check_null(addspp_na_sq_table)

```


```{r cwd_tab, echo = FALSE, eval = include_cwd_tab, results = 'asis'}
cat("### CWD {.tabset}", "\n")

```

```{r cwd_tables, echo = FALSE, eval = include_cwd_tab}
check_null(cwd_ns_table)

check_null(cwd_ns_missing_notes_table)

check_null(cwd_pm_table)

check_null(cwd_check3_table)

check_null(cwd_99_table)

check_null(cwd_data_99_table)
```

```{r plantID_tab, echo = FALSE, eval = include_plantID_tab, results = 'asis'}
cat("### Plant ID {.tabset}", "\n")

```
<details open><summary class='drop'><h3>Species new to plot</h3></summary>
```{r plantID_tables1, echo = FALSE, eval = include_plantID_tab}
check_null(spp_newplot_table)
```
</details>

<details open><summary class='drop'><h3>Species new to park</h3></summary>
```{r plantID_tables2, echo = FALSE, eval = include_plantID_tab}
check_null(spp_newpark_table)
```
</details>

<details open><summary class='drop'><h3>Potentially incorrect IDs</h3></summary>
```{r}
check_null(sppID_table) # Updated for MIDN species
```
</details>
<br>
<br>

```{r ISED_tab, echo = FALSE, eval = include_ISED_tab, results = 'asis'}
cat("### Early Detections {.tabset}", "\n")

```

```{r ISED_tables, echo = FALSE, eval = include_ISED_tab}
check_null(ised_table)
```



