---
output: 
  html_document:
    css: www/styles_weeklyQC.css
    anchor_sections: FALSE
    includes:
        in_header: "header_manual.html"
params:
  week_start: "2019-07-01"
---
Weekly QC Report for week starting: <span style="font-weight:bold;">`r params$week_start`</span> {.tabset .tabset-pills}
--------------------------------------------------
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

```{r import, include = FALSE, cache = TRUE}
#forestNETN::importData()
path = "C:/Forest_Health/exports/NETN"
forestNETN::importCSV(path = path, zip_name = "NETN_Forest_20210507.zip") # migration check 5/7
```

```{r deps, include = FALSE}
library(forestNETN)
library(tidyverse)
library(lubridate)
library(knitr)
library(kableExtra)
```

```{r compile}
curr_year <- year(params$week_start)
week_start <- as_date(params$week_start)
source("Compile_for_weekly_QC.R")
```

### QC Checks {.tabset}
#### Summary {.tabset}
This tab documents the Quality Control checks that were performed and number of suspect records returned for each database tab. For any suspect record returned, a separate tab is included in the report to review the data in question.

<details open><summary><h2>Stand</h2></summary>
</details>

<details open><summary><h2>Tree</h2></summary>

<details open class="indent"><summary><h3>Tree Data</h3></summary>
</details>

<details open class="indent"><summary><h3>Foliage Conditions</h3></summary>
</details>

<details open class="indent"><summary><h3>Conditions</h3></summary>
</details>
</details>

<details open><summary><h2>Microplot</h2></summary>
<details open class="indent"><summary><h3>Saplings</h3></summary>
</details>
<details open class="indent"><summary><h3>Seedlings</h3></summary>
</details>
<details open class="indent"><summary><h3>Shrubs</h3></summary>
</details>
</details>

<details open><summary><h2>Quadrats</h2></summary>
<details open class="indent"><summary><h3>Quadrat Data</h3></summary>
</details>
<details open class="indent"><summary><h3>Quadrat Species</h3></summary>
</details>
</details>

<details open><summary><h2>Additional Species</h2></summary>
</details>

<details open><summary><h2>CWD</h2></summary>
</details>

<details open><summary><h2>Soil</h2></summary>
</details>

```{r visit_notes, echo = FALSE, include = include_visit_notes, results = 'asis'}
cat("#### Visit Notes {.tabset}", "\n")
if(include_visit_notes == TRUE){
visit_table
  }
```

### Stand 

<h3>Stand Characteristics</h3>

### Tree {.tabset}

#### Tree Data {.tabset}

#### Conditions 

#### Foliage Conditions 

### Microplot {.tabset}

#### Saplings {.tabset}

#### Shrubs

#### Seedlings

### Quadrats {.tabset}

#### Quadrat Data {.tabset}

#### Quadrat Species

### Additional Species

### CWD

### Soil




